---
output: pdf_document
params:
  type: ''
  KTT_data: NA
  plot_data: NA
  title: ''
  filename: ''
---

# Trend Report
<p>&nbsp;</p>
```{r, comment="", warning=FALSE, message=FALSE, echo=FALSE}
cat('Report Date & Time: ', as.character(Sys.time()))
cat('Data File Name: ', params$filename)
cat('Report Title: ', params$title)
```
<p>&nbsp;</p>
Open UCL is licensed under a Creative Commons Attribution-NonCommercial- ShareAlike 4.0 International License and is the work of T. Chambers, A. Mikov and M. Salmon. Under the license terms you are free to:

**Share** — copy and redistribute the material
in any medium or format

**Adapt** — remix, transform, and build upon
the material

**Attribution** — You must give appropriate
credit, provide a link to the license,
and indicate if changes were made. You
may do so in any reasonable manner, but
not in any way that suggests the
licensor endorses you or your use.

**Non-Commercial** — You may not use the
material for commercial purposes.

**ShareAlike** — If you remix, transform, or
build upon the material, you must distribute
your contributions under the same license
as the original.

We encourage the reporting of bugs, issues, new ideas and contributions. If you want to report a bug, issue or have an idea to add to Open UCL you can email openstatsonline@gmail.com. Or if you are on github you can also use this link to post an issue on the Open UCL Repository.

\newpage
```{r, warning=FALSE, message=FALSE, echo=FALSE, results="asis"}
params$KTT_data %>%
  mutate(across(where(is.numeric), ~as.character(round(., 2)))) %>%
  pivot_longer(cols = -c(id, analyte), names_to = 'Characteristic') %>%
  group_split(id, analyte, .keep = FALSE) -> list_KTT

# params$KSTT_data %>%
#   pivot_longer(cols = -c(id, analyte), names_to = 'Characteristic') %>%
#   mutate(value = round(value, 2)) %>%
#   group_split(id, analyte, .keep = FALSE) -> list_KSTT
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, results="asis", fig.width = 8, fig.height = 8}
for(i in seq_along(list_KTT)) {
  cat("\n")
  
  
  
# This section creates new rows as defacto headings and then inserts to tmp table using rbind. This is a temporary workaround
  new_row1 = c("Kendall Trend Test Results Continuous", " ")
  new_row2 = c("Kendall Trend Test Results Seasonal", " ")
  plot1 <- params$plot_data$plot1[[i]]
  plot2 <- params$plot_data$plot2[[i]]
  
  print(knitr::kable(tibble(sprintf('      Report for ID : %s and Analyte : %s\n', params$KTT_data$id[i], params$KTT_data$analyte[i])), col.names = NULL, row.names = FALSE))
 # print(knitr::kable(list(rbind(new_row1, list_KTT[[i]]), rbind(new_row2, #list_KSTT[[i]])), col.names = NULL))
    print(knitr::kable(list(rbind(new_row1, list_KTT[[i]])), col.names = NULL))

  grid.arrange(plot1, plot2, ncol=2,
             heights=unit(c(10,10), c("cm", "cm")))
  cat("\n\\newpage\n")
}
```

