---
#title: "Open UCL Report Rev8.1"
output: pdf_document
params:
  type: ''
  data: NA
  title: ''
  filename: ''
  dropdown: ''
  my_qqplot: NA
  my_qqplotlog: NA
  my_boxplot: NA
  my_hist: NA
---
# Open UCL Report Rev8.1 (Open UCL Beta Ver 3.02)
<p>&nbsp;</p>
```{r, comment="", warning=FALSE, message=FALSE, echo=FALSE}
cat('Report Date & Time: ', as.character(Sys.time()))
cat('Data File Name: ', params$filename)
cat('Report Title: ',params$title)
```
<p>&nbsp;</p>
Open UCL is licensed under a Creative
Commons Attribution-NonCommercial-
ShareAlike 4.0 International License and is
the work of **T. Chambers, A. Mikov and M. Salmon**.
Under the license terms you are free to:

**Share** — copy and redistribute the material
in any medium or format

**Adapt** — remix, transform, and build upon
the material

**Attribution** — You must give appropriate
credit, provide a link to the license,
and indicate if changes were made. You
may do so in any reasonable manner, but
not in any way that suggests the
licensor endorses you or your use.

**Non-Commercial** — You may not use the
material for commercial purposes.

**ShareAlike** — If you remix, transform, or
build upon the material, you must distribute
your contributions under the same license
as the original.

We encourage the reporting of bugs,
issues, new ideas and contributions. If
you want to report a bug, issue or have
an idea to add to Open UCL you can email
**openstatsonline@gmail.com**. Or if you
are on github you can also use this link
**<link to be inserted>** to post an
issue on the Open UCL Repository.


\newpage
```{r, warning=FALSE, message=FALSE, echo=FALSE, results="asis"}
for(i in names(params$data)) {
  #cat('Report for Analyte (',i,')', '\n') # This line is meant to place a page heading but on some computers the heading appers aftre the first tables in the middle of the page. Workaround is below using a Kable table
  cat("\n")

    tmp <- params$data[[i]] %>%
            mutate(across(.fns = as.character)) %>%
            pivot_longer(cols = everything(), names_to = 'Characteristic')

# This section creates new rows as defacto headings and then inserts to tmp table using rbind. This is a temporary workaround
  new_row1 = c("Descriptive Stats", " ")
  new_row2 = c("Log Transformed", " ")
  new_row3 = c("Normality Tests", " ")
  new_row4 = c("Upper Conf Limits", " ")
  new_row5 = c("Other Results", " ")

  tmp = rbind(tmp[1, ], new_row1, tmp[- (1), ])
  tmp = rbind(tmp[1:13, ], new_row2, tmp[- (1:13), ])
  tmp = rbind(tmp[1:18, ], new_row3, tmp[- (1:18), ])
  tmp = rbind(tmp[1:23, ], new_row4, tmp[- (1:23), ])
  tmp = rbind(tmp[1:29, ], new_row5, tmp[- (1:29), ])

  print(knitr::kable(list(tmp[c(1), 2]), col.names = NULL, row.names = FALSE)) #interim solution for page headings is a kable table but limited to a single value row 1 col 2 with col names = NULL and row names FALSE. Although it seems to work well enough.
  print(knitr::kable(list(tmp[c(2:4, 5:18, 19:23), ], tmp[c(24:38), ]), col.names = NULL))


  grid.arrange(params$my_qqplot[[i]], params$my_qqplotlog[[i]], params$my_boxplot[[i]], params$my_hist[[i]], ncol=2,
             heights=unit(c(47,47), c("mm", "mm")))
  cat("\n\\newpage\n")
}
```
